---
title: "Homework 5"
output: github_document
---


# Problem 1

```{r setup, include = FALSE}
library(tidyverse)
library(broom)
library(purrr)

```

```{r data_summary}
set.seed(1)

birthdays_shared <- function(n) {
  birthdays <- sample(1:365, n, replace = TRUE)
  return(length(unique(birthdays)) < n)
}

group_sizes <- 2:50
probabilities <- numeric(length(group_sizes))

another_experiment <- function(n, number, birthdays_shared) {
  x = 0
  for(i in 1:number){
    birthdays_shared(n)
    
    if(birthdays_shared(n) == TRUE){
      x = x + 1
    }
    else{
      x = x
    }
  }
  x
}

for (i in 2:50) {
  number_of_successes <- another_experiment(i, 10000, birthdays_shared(i))
  probabilities[i-1] <- number_of_successes/10000
}

birthday_df <- data.frame(
  group_size = group_sizes,
  probability = probabilities
)

birthday_df |> ggplot(aes(x = group_size, y = probability)) +
  geom_point() + geom_line() +
  labs(x = "Sample Size",
       y = "Probability of 2 or More People Sharing a Birthday",
       title = "Probability of Shared Birthdays with 1000 simulations per Sample Size")

```


As the group size increases, the probability that at least two people share the same birthday also increases. Notably, at around a group size of 23 people, such probability crosses the 0.5 threshold. Finally, even at around a group size of 45 to 50, the probability is already approaching a value of 1.0.

# Problem 2

```{r data_size}
ncol(early_january_weather)
nrow(early_january_weather)
```

The size of this data set would have a total of 15 variables and 358 values for each variable. The mean temperature in early January would be 39.58 degrees Fahrenheit.

```{r scatter_plot}
ggplot(data = early_january_weather, aes(x=time_hour, y=temp, color = humid)) + geom_point() 

ggsave("scatter_plot.pdf", height = 4, width = 4)
```


# Section 2

I can take the mean of the sample, too!

```{r dataframes}

dataframe = tibble(
  normal_distribution = rnorm(10),
  logical_vector = (normal_distribution > 0),
  vec_char = c("My", "name", "is", "Richard", "and", "I", "like", "watching", "TV", "shows"),
  factor_vector = factor(vec_char, c("low", "medium", "high"))
)

```

```{r dataframe mean}
  norm_mean = mean(dataframe$normal_distribution)
  logical_mean = mean(dataframe$logical_vector)
  
```

The mean of the normal distribution is `r mean(dataframe$normal_distribution)`.
The mean of the whole logical vector is `r mean(dataframe$logical_vector)`.

```{r dataframe_mean_2}
  vector_mean = mean(dataframe$vec_char)
  factor_mean = mean(dataframe$factor_vector)
```

# Section 3
