---
title: "Homework 1"
output: html_document
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r setup, include = FALSE}
library(tidyverse)
```

```{r data_summary}
library(moderndive)
data("early_january_weather")
summary(early_january_weather)
mean(early_january_weather$temp)
```

```{r data_size}
ncol(early_january_weather)
nrow(early_january_weather)
```

The size of this data set would have a total of 15 variables and 358 values for each variable. The mean temperature in early January would be 39.58 degrees Fahrenheit.

```{r scatter_plot}
ggplot(data = early_january_weather, aes(x=time_hour, y=temp, color = humid)) + geom_point() 

ggsave("scatter_plot.pdf", height = 4, width = 4)
```


# Section 2

I can take the mean of the sample, too!

```{r dataframes}

dataframe = tibble(
  normal_distribution = rnorm(10),
  logical_vector = (normal_distribution > 0),
  vec_char = c("My", "name", "is", "Richard", "and", "I", "like", "watching", "TV", "shows"),
  factor_vector = factor(vec_char, c("low", "medium", "high"))
)

```

```{r dataframe mean}
  norm_mean = mean(dataframe$normal_distribution)
  logical_mean = mean(dataframe$logical_vector)
  
```

The mean of the normal distribution is `r mean(dataframe$normal_distribution)`.
The mean of the whole logical vector is `r mean(dataframe$logical_vector)`.

```{r dataframe_mean_2}
  vector_mean = mean(dataframe$vec_char)
  factor_mean = mean(dataframe$factor_vector)
```

# Section 3
